Clustering `SCPCL000822` and `SCPCL000824`

### 2024-08-05 analyses/cell-type-ewings/exploratory_analysis/05-cluster-exploration.Rmd
spelling updates

---
title: "Clustering SCPCL000822 and SCPCL000824"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    code_folding: "hide"
---

>>>>

---
title: "Clustering `SCPCL000822` and `SCPCL000824`"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    code_folding: "hide"
---
